\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{etaremune}
\usepackage{fixltx2e}
\usepackage{color}
\usepackage{verbatim}
\definecolor{unlred}{rgb}{0.81,0.0,0.0}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{setspace}
% Set your name here
\def\name{CHENYONG MIAO}

%Add in-line comments
\newcommand{\ignore}[1]{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = unlred,
  pdfauthor = {\name},
  pdfkeywords = {comparative genomics, GWAS, ASE},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

\centerline{\huge \textsc{Curriculum Vitae}}
\vspace{0.25in}
\centerline{\huge \textsc{\name}}


\vspace{0.25in}

%ADDRESS
%Update This with you own information
\begin{minipage}{0.5\linewidth}
  \begin{center}
  \href{http://bigdata.unl.edu/}{Quantitative Life Sciences Initiative}\\
  \href{http://www.unl.edu/psi/}{Center for Plant Science Innovation}\\
  \href{http://agronomy.unl.edu}{Department of Agronomy \& Horticulture}\\
  \href{http://www.unl.edu}{University of Nebraska-Lincoln} \\
\end{center}
\end{minipage}
\begin{minipage}{0.5\linewidth}
  \begin{center}
  \begin{tabular}{ll}
    Office: & N231 Beadle Center \\
    Phone: & (402) 310-2755 \\
    Email: & \href{mailto:cmiao@huskers.unl.edu}{cmiao@huskers.unl.edu} \\
    Web: & \href{http://www.schnablelab.org/}{schnablelab.org} \\
  \end{tabular}
\end{center}
\end{minipage}

%EMPLOYMENT
%Grad Students and Undergrads should delete this section. Postdocs should list postdoc positions here
\section*{Employment}
\begin{itemize}
\item Research Assistant, Department of Agronomy and Horticulture, University of Nebraska-Lincoln 2016-present.
\item Research Assistant, Genomics and Biotechnology Center, Fujian Agriculture and Forestry University 2013-2016.
\end{itemize}

%EDUCATION
%For a degree program you are currently enrolled in write the date as 2010-Present
\section*{Education}
\begin{itemize}
 \item Graduate Agronomy (with James C. Schnable), University of Nebraska-Lincoln 2016-present.
 \item MS Bioinformatics (with Haibao Tang), Fujian Agriculture and Forestry University 2013-2016.
 \item BA Biotechnology, Henan University of Science and Technology 2009-2013.
\end{itemize}

%Comment out this section if you don't have items to put here
%List any small grants (travel awards etc), being selected at poster presentations, etc
%Students who are or have been supported by a fellowship can list it here
%\section*{Honors and Awards}
%\begin{itemize}
%\item Research Assistantship, 2016-present.
%\end{itemize}

%PUBS

\section*{Publications} 
%\begin{center}
%Replace with link to your own google scholar page if you have one. 
%\href{https://scholar.google.com/citations?user=IQOpemkAAAAJ}{Google Scholar} \\
%\end{center}
%SUBMITTED
\begin{etaremune}
\item Ray Ming, Robert VanBuren, Ching Man Wai, Haibao Tang, ...{\bf Chenyong Miao}, ... Robert E Paull, Qingyi Yu (70 total authors). (2015) The pineapple genome and the evolution of CAM photosynthesis. \textsc {Nature Genetics} doi: \href{http://www.nature.com/ng/journal/v47/n12/full/ng.3435.html}{10.1038/ng.3435}.
\item Haibao Tang, Xingtan Zhang, {\bf Chenyong Miao}, Jisen Zhang, Ray Ming, James C Schnable, Patrick S Schnable, Eric Lyons, Jianguo Lu. (2015) ALLMAPS: robust scaffold ordering based on multiple maps. \textsc {Genome Biology} doi: \href{http://genomebiology.biomedcentral.com/articles/10.1186/s13059-014-0573-1}{10.1186/s13059-014-0573-1}.
\item Jingping Fang, {\bf Chenyong Miao}, Rukai Chen, Ray Ming. (2016) Genome-Wide Comparative Analysis of Microsatellites in Pineapple. \textsc {Tropical Plant Biology} doi: \href{https://link.springer.com/article/10.1007/s12042-016-9163-6}{10.1007/s12042-016-9163-6}.
\end{etaremune}
\subsection*{Manuscripts in Review}
\begin{etaremune}
\item Jiandong Bao, Meilian Chen, Wei Tang, Zhenhui Zhong, Lianyu Lin, Xingtan Zhang, {\bf Chenyong Miao}, Haibao Tang, Jishen Zhang, Guodong Lu, Ray Ming, Justice Norvienyeku, Baohua Wang, Zonghua Wang. PacBio sequencing provides new insights into Magnaporthe oryzae genome structure.
\item Jisen Zhang, Qing Zhang, Leiting Li, Haibao Tang, Qiong Zhang, Yang Chen, Jie Arro, Aiqin Wang, {\bf Chenyong Miao}, Ray Ming. Dissecting the Recent Polyploidization in Saccharum Founding Species Based on Transcriptome Sequencing.
\item {\bf Chenyong Miao}, Jingping Fang, Pingping Liang, Xingtan Zhang, James C. Schnable, Haibao Tang. Genotype-Corrector: improved genotype calls for genetic mapping.
\end{etaremune}


%OTHER PUBS
%Book chapters and that short of thing. Most of you can skip this section.
\section*{Poster Presentations}
\begin{etaremune}
\item {\bf Chenyong Miao}, Jinliang Yang, James Schnable. (2017) Comparative GWAS in \textit{Sorghum bicolor} and \textit{Setaria italica}. 59th Maize Genetics Conference. St. Louis, Missouri. 
\end{etaremune}

\end{document}
